### 2017-07-20 README.Rmd

@@

>>>>

One numerical variable (standard deviation)

```
mtcars %>%
  specify(response = mpg) %>% # alt: mpg ~ NULL (or mpg ~ 1)
  hypothesize(null = "point", sigma = 5) %>% 
  generate(reps = 100, type = "bootstrap") %>% 
  calculate(stat = "sd")
```

@@

One numerical (standard deviation)

```
mtcars %>%
  specify(response = mpg) %>%
  generate(reps = 100, type = "bootstrap") %>%
  calculate(stat = "sd")
```
